DRAFT: Social Learning and Shared Belief: The Importance of Bias and Trust for Information Diffusion

### 2014-07-08 paper/paper.tex
remove authors
correct posteriors

\title{DRAFT: Social Learning and Shared Belief: The Importance of Bias and Trust for Information Diffusion}
\author{Bryan Kelly, Joseph Leland Bybee}
\date{\today}

@@

\subsection{Posterior Specification for $z_i$}

\[p(z_i | w_i, \theta, \phi) \propto p(z_i = k | \theta) p(w_i | z_i = k, \phi)\]

\[= \frac{\theta_k}{\sum_k \theta} \frac{\phi_{k, w_i}}{\sum_v \phi_k}\]

@@

\[= N(\beta_t, b^2I) N(\beta_{t-1}, \sigma^2I)\]

\[\propto \exp{\left(-\frac{1}{2}[(\phi - \beta_t)^T(\phi - \beta_t) + (\beta_t - \beta_{t-1})^T(\beta_t - \beta_{t-1})]\right)}\]

@@

\subsection{Posterior Specification for $\alpha_t$}

@@

\[= N(\alpha_{it}, a^2I) N(\text{\boldmath$\alpha$}_{t-1}^T \gamma_i, \delta^2I)\]

\[\propto \exp{\left(-\frac{1}{2}[(\theta - \alpha_{it})^T(\theta - \alpha_{it}) + (\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i)^T(\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i)]\right)}\]

@@

\subsection{Posterior Specification for $\gamma$}

@@

\[= N(\text{\boldmath$\alpha$}_{t-1}^T \gamma_i, \delta^2I)N(\mu, \xi^2)\]

\[\propto \exp{\left(-\frac{1}{2}[(\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i)^T(\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i) + (\gamma_i - \mu)^T(\gamma_i - \mu)]\right)}\]

@@

\subsection{Posterior Specification for $\theta$}

\[p(\theta | z, \alpha_{it}, \delta^2) \propto p(z | \theta) p(\theta | \alpha_{it}, \delta^2)\]

\[= Mult(\pi(\theta)) N(\alpha_{it}, \delta^2I)\]

\[\propto \left(\prod_{i=1}^N \prod_{k=1}^K \frac{\theta_k^{I_{z_i}=k}}{\sum_k \theta}\right) \left(\exp{-\frac{1}{2}(\theta - \alpha_{it})^T(\theta - \alpha_{it})}\right) \]

@@

\subsection{Posterior Specification for $\phi$}

\[p(\phi_k | \beta_t, z, w, b^2) \propto p(w | \phi_k, z) p(\phi_k | \beta_t)\]

\[= Mult(\pi(phi_{k,z})) N(\beta_t, b^2)\]

\[\propto \left(\prod_{i:z_i=k}^N \prod_{v=1}^V \frac{\phi_{k, v}^{I_{w_i}=v}}{\sum_v \phi_k}\right) \left(\exp{-\frac{1}{2}(\phi_k - \beta_t)^T(\phi_k - \beta_t)}\right) \]

>>>>

\title{DRAFT: Social Learning and Shared Belief: The Importance of Bias and Trust for Information Diffusion}
\date{\today}

@@

\subsection{Posterior Specification for $z_{jit}$}

\[p(z_{jit} | w_{jit}, \theta_{it}, \phi_t) \propto p(z_{jit} = k | \theta_{it}) p(w_{jit} | z_{jit} = k, \phi_t)\]

\[= \frac{\theta_{it}^{I_{z_{jit}}=k}}{\sum_k \theta_{it}} \frac{\phi_{kt}^{I_{w_j}=v}}{\sum_v \phi_{kt}}\]

@@

\[=  \prod_{k=1}^K N(\beta_t, b^2I) N(\beta_{t-1}, \sigma^2I)\]

\[\propto \exp{\left(\sum_{k=1}^K(\phi_k - \beta_{t})^T(\phi_k - \beta_{t}) + (\beta_{t} - \beta_{t-1})^T(\beta_{t} - \beta_{t-1})\right)}\]

@@

\subsection{Posterior Specification for $\alpha_{it}$}

@@

\[= \prod_{d=1}^{D_i} N(\alpha_{it}, a^2I) N(\text{\boldmath$\alpha$}_{t-1}^T \gamma_i, \delta^2I)\]

\[\propto \exp{\left(\sum_{d=1}^{D_i}(\theta_d - \alpha_{it})^T(\theta_d - \alpha_{it}) + (\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i)^T(\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i)\right)}\]

@@

\subsection{Posterior Specification for $\gamma_i$}

@@

\[= \prod_{t=2}^T N(\text{\boldmath$\alpha$}_{t-1}^T \gamma_i, \delta^2I)N(\mu, \xi^2)\]

\[\propto \exp{\left(\sum_{t=2}^T(\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i)^T(\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i) + (\gamma_i - \mu)^T(\gamma_i - \mu)\right)}\]

@@

\subsection{Posterior Specification for $\theta_{it}$}

\[p(\theta_{it} | z, \alpha_{it}, \delta^2) \propto p(z | \theta_{it}) p(\theta_{it} | \alpha_{it}, \delta^2)\]

\[= \prod_{d=1}^D \prod_{j=1}^{J_d} Mult(\pi(\theta_{dit}))\prod_{d=1}^D N(\alpha_{it}, \delta^2I)\]

\[\propto \left(\prod_{d=1}^D \prod_{j=1}^{J_d} \frac{\theta_{dit}^{I_{z_j}=k}}{\sum_k \theta_{dit}}\right) \exp{\left(\sum_{d=1}^D(\theta_{dit} - \alpha_{it})^T(\theta_{dit} - \alpha_{it})\right)} \]

@@

\subsection{Posterior Specification for $\phi_t$}

\[p(\phi_t | \beta_t, z, w, b^2) \propto p(w | \phi_t, z) p(\phi_t | \beta_t)\]

\[= \prod_{k=1}^K \prod_{j=1}^{J_k} Mult(\pi(\phi_{kt}))\prod_{k=1}^K N(\beta_t, b^2)\]

\[\propto \left(\prod_{k=1}^K \prod_{j=1}^{J_k} \frac{\phi_{kt}^{I_{w_j}=v}}{\sum_v \phi_{kt}}\right) \exp{\left(\sum_{k=1}^K(\phi_{kt} - \beta_t)^T(\phi_{kt} - \beta_t)\right)}\]
